---
output: github_document
keep-md: true
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `ggirf`
This package provides ggplot2 support for impulse response analysis in various packages such as `vars`, `lpirfs`, `BGVAR` used for macroeconomic analysis. The library includes custom colors and a ggplot2 theme. You can optionally provide different colors.

## Installation
You can install the development version of `ggirf` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("muhsinciftci/ggirf")
```

## Contribution
Should you want to contribute to this package, please make a pull request via this repo

## VAR impulse response analysis via `vars` package
```{r}
library(vars)
library(tidyverse)
library(ggirf)
```

```{r}
var_estimation <- VAR(Canada, p = 2, type = "const")
var_irf        <- irf(var_estimation, impulse = 'e')
```

and the impulse response graph via `ggirf` would be:
```{r}
gg_vars(irf_result = var_irf, var_shock = 'e', line_color = 'black', shade_color = gg_colors[7]) +
  gg_theme_irf()
```
or you can simply provide one variable as well. **Providing multiple shocks once is not allowed.**




















